Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-10 volunteer-clouds-ieee-ci-si.tex
Fixing a few typos

There is, then, space for systems that do not have any of these
assumptions, such as the one presented in this paper, which will be
provisionally named {\sf NodIO}. {\sf NodIO} is first an application that
runs in two tiers, a server and a client, the latter  can be possibly
run on a  % [Pedro] Both the server and the client in browsers?
          % different browsers as I understand? [JJ]  No, server in
          % server, client in browser, although there's nothing that
          % can't be done in a browser.
browser. As such, it can be run in any computer that loads the web
page where the client is embedded, including many over which%[Mario]Quitar el possibly?   [JJ] Done
the scientist has no control.

@@

The main problem with Java and all the other browser-embedded
technologies is that they are not {\em universal} in the
sense than an extra component, namely, the Java virtual machine or another
virtual environment has to be installed in the browser.
Also these virtual environments have become targets of malicious attacks; 
for instance numerous vulnerabilities have been discovered in 
the proprietary Adobe Flash runtime environment and
video player \cite{ford2009analyzing,watanabe2010new}. The need for
these additional environments has been mitigated with the
adoption of the HTML5 standard \cite{anthes2012html5}.
JavaScript, however,
\cite{flanagan2006javascript} was introduced in 1997 as a
browser-embedded language and has, since then, become a set of standards
\cite{ECMA-262} that include the language and its components. Since
early on, it was adopted by the industry and also by scientists,
who used them for creating an EA on
the browser as early as 1998 \cite{jj-ppsn98}.

@@

A sequence diagram of the W$^2$ version of {\sf NodIO} is presented
in Figure~\ref{fig:system:w2}. In this version, clients use the Web Workers
API to run two NodEO instances per browser. The sequence diagram shows the
interaction between processes in a time sequence. In this system there are
two kinds of asynchronous messages: HTTP Requests shown as bold arrows between
the client and the server where PUT and GET HTTP Methods are represented by
red and blue arrows respectively. There are also messages between workers and
the main thread in locally in the client, these are shown as thin solid arrows.
There are three processes involved:
\begin{itemize}
\item {\em nodejs} This is the server side process which is basically
  the same as used previously, except for some minor log-related
  changes. 
\item {\em Client main thread}  This process handles the user interaction
using the JQuery framework. The Chart.js library is used to display a chart of
the best fitness in the population over time. The main script also creates
worker instances and handles the user interface.
\item {\em Worker global scope} The worker execution space does not have
access to the Document Object Model (DOM) or JQuery objects in the main thread.
Asynchronous HTTP requests to the server are implemented using the XHR object. %FERGU: Qué es el objeto XHR? Alguna referencia/justificación de por qué se usa?
\end{itemize}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=4in]{img/Algorithm.pdf}
\caption{Description of the W$^2$ version of {\sf NodIO}. In this
  version, clients use Web Workers to run the evolutionary algorithm,
  with two of them per browser.}
\label{fig:system:w2}
\end{figure}

@@

Although we think that, in general, the results presented in this
paper are independent of the problem chosen, it is true that even if
it a difficult problem for evolutionary algorithms, it takes a few
seconds with the right settings to solve. This makes it difficult also
for this kind of asynchronous framework, but it would be interesting
to check the performance for more computationally demanding
tasks. Besides, the two versions of the framework include as an
algorithmc variant using random population size. We do not think this
has had a big influence on the result, but it would be interesting to
measure exactly what this influence has been. Adding a bit of more
control to the user might contribute also to gamification. Right now
the user has only two webworkers. It is a matter of a single click to
open more tabs in the browser, giving more webworkers, but it would be
interesting to put everything in a single page and under our control,
to check how often this happens and under which conditions.

>>>>

There is, then, space for systems that do not have any of these
assumptions, such as the one presented in this paper, which will be
provisionally named {\sf NodIO}. {\sf NodIO} is first an application that
runs in two tiers, a server and a client, the latter  can be possibly
run on a  % [Pedro] Both the server and the client in browsers?
          % different browsers as I understand? [JJ]  No, server in
          % server, client in browser, although there's nothing that
          % can't be done in a browser.
browser. As such, it can be run in any computer that loads the web
page where the client is embedded, including many over which %[Mario]Quitar el possibly?   [JJ] Done
the scientist has no control.

@@

The main problem with Java and all the other browser-embedded
technologies is that they are not {\em universal} in the
sense than an extra component, namely, the Java virtual machine or another
virtual environment has to be installed in the browser.
Also these virtual environments have become targets of malicious attacks; 
for instance numerous vulnerabilities have been discovered in 
the proprietary Adobe Flash runtime environment and
video player \cite{ford2009analyzing,watanabe2010new}. The need for
these additional environments has been mitigated with the
adoption of the HTML5 standard \cite{anthes2012html5}.
JavaScript, however,
\cite{flanagan2006javascript} 
%was introduced in 1997 as a 
%browser-embedded language and has, since then,
%Ya se había dicho  
has become a set of standards
\cite{ECMA-262} that include the language and its components. Since
early on, it was adopted by the industry and also by scientists,
who used them for creating an EA on
the browser as early as 1998 \cite{jj-ppsn98}.

@@

A sequence diagram of the W$^2$ version of {\sf NodIO} is presented
in Figure~\ref{fig:system:w2}. In this version, clients use the Web Workers
API to run two NodEO instances per browser. The sequence diagram shows the
interaction between processes in a time sequence. In this system there are
two kinds of asynchronous messages: HTTP Requests shown as bold arrows between
the client and the server where PUT and GET HTTP Methods are represented by
red and blue arrows respectively. There are also messages between workers and
the main thread locally in the client, these are shown as thin solid arrows.
There are three processes involved:
\begin{itemize}
\item {\em node.js} This is the server side process which is basically
  the same as used previously, except for some minor log-related
  changes. 
\item {\em Client main thread}  This process handles the user interaction
using the JQuery framework. The chart.js library is used to display a chart of
the best fitness in the population over time. The main script also creates
worker instances and handles the user interface.
\item {\em Worker global scope} The worker execution space does not have
access to the Document Object Model (DOM) or JQuery objects in the main thread.
Asynchronous HTTP requests to the server are implemented using the XHR object. %FERGU: Qué es el objeto XHR? Alguna referencia/justificación de por qué se usa?
\end{itemize}
%
\begin{figure}[!htb]
\centering
\includegraphics[width=4in]{img/Algorithm.pdf}
\caption{Description of the W$^2$ version of {\sf NodIO}. In this
  version, clients use Web Workers to run the evolutionary algorithm,
  with two of them per browser.}
\label{fig:system:w2}
\end{figure}

@@

Although we think that, in general, the results presented in this
paper are independent of the problem chosen, it is true that even if
it is a difficult problem for evolutionary algorithms, it takes a few
seconds with the right settings to solve. This makes it difficult also
for this kind of asynchronous framework, but it would be interesting
to check the performance for more computationally demanding
tasks. Besides, the two versions of the framework include as an
algorithmc variant using random population size. We do not think this
has had a big influence on the result, but it would be interesting to
measure exactly what this influence has been. Adding a bit of more
control to the user might contribute also to gamification. Right now
the user has only two webworkers. It is a matter of a single click to
open more tabs in the browser, giving more webworkers, but it would be
interesting to put everything in a single page and under our control,
to check how often this happens and under which conditions.
